### 2018-11-28 README.Rmd
Adds comparing simplify = FALSE for metadata table
Also regenerated the README.md.

```{r}
data(bird.orders)
nexml_write(bird.orders, "test.xml")
```

@@

```{r } 
birds <- nexml_read("test.xml")
get_taxa(birds)
get_metadata(birds) 
```

@@

This next block defines a resource (link), described by the `rel` attribute as a homepage, a term in the `foaf` vocabulalry.  Becuase `foaf` is not a default namespace, we will have to provide its URL in the full definition below.

@@

For this kind of richer annotation, it is best to build up our NeXML object sequentially. Frist
we will add `bird.orders` phylogeny to a new phylogenetic object, and then we will add the metadata
elements created above to this object. Finally, we will write the object out as an XML file:

>>>>

```{r}
data(bird.orders)
nexml_write(bird.orders, "test.xml", creator = "Carl Boettiger")
```

@@

```{r } 
birds <- nexml_read("test.xml")
get_taxa(birds)
get_metadata(birds, simplify = FALSE)
```

By default, the table of metadata annotations is simplified by combining
`property` and `rel` into `property`, and the identifiers into `Meta`:
```{r } 
get_metadata(birds)
```

@@

This next block defines a resource (link), described by the `rel` attribute as a homepage, a term in the `foaf` vocabulalry.  Because `foaf` is not a default namespace, we will have to provide its URL in the full definition below.

@@

For this kind of richer annotation, it is best to build up our NeXML object sequentially. First
we will add `bird.orders` phylogeny to a new phylogenetic object, and then we will add the metadata
elements created above to this object. Finally, we will write the object out as an XML file:
